---
title: "Exchange rates"
output: 
  html_document:
    self_contained: no
---

# Introduction

This is a report showing tabular and graphical comparison of the two selected currencies

```{r echo=FALSE, eval=TRUE, cache=FALSE, warning=FALSE, message=FALSE}

library(yaml)
library(knitr)
library(reshape)
library(ggplot2)
library(plotly)
library(DT)
library(googleVis)

source("data_loader.r")
comparisonFrame = cF
seriesHelperFrame = sHF
mapHelperFrame = mHF


```

# Comparison table of `r params$curr1` & `r params$curr2`

```{r , results='asis', echo=F, cache=FALSE, warning=FALSE, message=FALSE}

tmpTab <- gvisTable(comparisonFrame, options=list(width = 900, height= 400))

print(tmpTab,"chart")

```

# Elements of visual comparoson of `r params$curr1` & `r params$curr2`

## Map

```{r , results='asis', echo=F, cache=FALSE, warning=FALSE, message=FALSE}

img <- gvisGeoChart(mapHelperFrame, locationvar="Entity", colorvar="CurrNo",
                     hovervar="Info",
                     options=list(projection="kavrayskiy-vii",width=800,height=800,
                                  colors="['#000000', '#FFD700']"))

print(img, "chart")

```


## Time series

```{r , results='asis', echo=F, cache=FALSE, warning=FALSE, message=FALSE}

img <- gvisLineChart(seriesHelperFrame, xvar="data",
                              options=list(width=800, height=800,
                                           colors="['#000000', '#FFD700']",
                                           title="Time series of selected currencies", 
                                           vAxis="{title:'Rate'}",
                                           hAxis="{title:'Date'}"))

print(img, "chart")

```

## Barplot of currency differences

```{r , results='asis', echo=F, cache=FALSE, warning=FALSE, message=FALSE}

if (params$curr1 != params$curr2) {
  
  df <- comparisonFrame
  df$difference = unlist(abs(df[2] - df[3]))
  
  img <- (
    ggplot(df, mapping = aes(x = difference)) +
    geom_histogram(color="#000000", fill="#FFD700") +
    ggtitle("Barplot of currency differences") + 
    xlab("Difference") + ylab("Frequency")
  )
  
  print(img)
  
} else {
  
  print("Currencies are duplicated. The plot will not be shown.")
  
}

```

## Scatterplot of selected currencies

```{r , results='asis', echo=F, cache=FALSE, warning=FALSE, message=FALSE}

if (params$curr1 != params$curr2) {

  df <- comparisonFrame
  img <- (
      ggplot(df, mapping = aes_string(x = names(df)[2], y = names(df)[3])) +
      geom_point() +
      scale_fill_manual(values=c('#000000','#FFD700')) + 
      ggtitle("Scatterplot of selected currencies") + 
      xlab(names(df)[2]) + ylab(names(df)[3])
  )
  
  print(img)

} else {
  
  print("Currencies are duplicated. The plot will not be shown.")
  
}

```

# Linear regression of `r params$curr1` & `r params$curr2`

**Stats and model summary.**:

```{r, results='asis', echo=F, eval=T, cache=FALSE, warning=FALSE, message=FALSE}

if (params$rflag) {
  
  
  if(nrow(comparisonFrame) && params$curr1 != params$curr2){
  
    df <- comparisonFrame
    colnames(df) <- c("data", "x", "y") 
    
    regressionModel = lm(formula = x ~ y, data = df)
    model_summary <- capture.output(summary(regressionModel))
    
    print(model_summary)
    
  } 
} 

```

**Rainbow test**:

```{r, results='asis', echo=F, eval=T, cache=FALSE, warning=FALSE, message=FALSE}

if (params$rflag) {
  
  
  if(nrow(comparisonFrame) && params$curr1 != params$curr2){
  
    df <- comparisonFrame
    colnames(df) <- c("data", "x", "y") 
    
    regressionModel = lm(formula = x ~ y, data = df)
    
    rtest <- raintest(regressionModel)
      
    cat("Statistic: ", rtest$statistic, "  \n")
    cat("Parameters (df1 & df2): ", rtest$parameter, "  \n")
    cat("p-value < ", rtest$p.value, "  \n")
  }
}
```

```{r , results='asis', echo=F, cache=FALSE, warning=FALSE, message=FALSE}

if (params$rflag) {
  
  
  if(nrow(comparisonFrame) && params$curr1 != params$curr2){

    img <- (
                      ggplot(df, mapping = aes_string(x = names(df)[2], y = names(df)[3]))
                      + geom_point()
                      + geom_smooth(method='lm',formula=y~x, colour="#FFD700") 
                      + ggtitle("Regression model - graphical representation") 
                      + xlab(params$curr1) + ylab(params$curr2)
                  )
    print(img)
  
  } else {
    
    print("Error while making the model. Currencies are duplicated.")
    
  }
} else {
  
  print("The option to create the model has not been activated.")
  
}

```
